---
title: "DDPW3A"
author: "RS"
date: "10 10 2020"
output: html_document
---

```{r setup, include=FALSE}
library(knitr)
library(dplyr)
library(plotly)
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

Create a web page presentation using R Markdown that features a plot created with Plotly. Host your webpage on either GitHub Pages, RPubs, or NeoCities. Your webpage must contain the date that you created the document, and it must contain a plot created with Plotly. We would love to see you show off your creativity! 

Print the current time:

```{r}
Sys.time()
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
myFigure <- plot_ly(
  type="treemap",
  labels=c("Eve", "Cain", "Seth", "Enos", "Noam", "Abel", "Awan", "Enoch", "Azura"),
  parents=c("", "Eve", "Eve", "Seth", "Seth", "Eve", "Eve", "Awan", "Eve")
)
myFigure
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
